Postural developments mediate children's visual access to social information

### 2018-01-28 writeup-cogsci/cogsci2018_faceOnly.tex
header edits

This second of the CNN-based algorithms--the pose detector--provided us
(along with other parts) with the location of an agent's wrists, which
we used as a good proxy for the presence of a hand. We did so first
because we did not capture the entire visual field experienced by the
infants/children. Thus, even though the video may only show the presence
of a wrist, the caregiver's hand may be within the child's field of
view. Second, we did so because hands are often occluded by objects when
caregivers are interacting with children, yet still visually accessible
by the child and part of their joint interaction. For example, if a
caregiver was holding a toy and presenting it to the infant, their
wrists may be visible but their hand may not necessarily be (as it is
occluded by the toy). Similarly, we used the nose (one of the 18 parts)
to operationalize face presence, as any half of a face necessarily
contains a nose.

@@

For face detection, MTCNN outperformed OpenPose when looking at the
composite F-score (0.89 vs.~0.83); thus the face presence analyses to
follow all result from MTCNN detections. We found that although MTCNN
and OpenPose perform comparably with the random sample, MTCNN performs
better on the high density sample evaluation (specifically looking at
precision), suggesting that OpenPose generated more false positives than
MTCNN. ViolaJones performed quite poorly relative to the other
detectors, finding much less faces in the random sample.

For wrist detection, OpenPose performed moderately well (f = 0.72) with
relatively high precision, but low recall on the randomly sampled set of
frames (see Table 2). We thus analyze wrist detections, with the caveat
that we are likely underestimating the proportion of wrists overall in
the datatset.

@@

\section{Changes in Access to Faces and
Hands}\label{changes-in-access-to-faces-and-hands}

@@

\subsection{Access to Faces and Wrists During Labeling
Events}\label{access-to-faces-and-wrists-during-labeling-events}

>>>>

This second of the CNN-based algorithms--the pose detector--provided us
(along with other parts) with the location of an agent's wrists, which
we used as a good proxy for the presence of a hand. We did so first
because we did not capture the entire visual field experienced by the
infants/children. Thus, even though the video may only show the presence
of a wrist, the caregiver's hand may be within the child's field of
view. Second, we did so because hands are often occluded by objects when
caregivers are interacting with children, yet still visually accessible
by the child and part of their joint interaction. For example, if a
caregiver was holding a toy and presenting it to the infant, their
wrists may be visible but their hand may not necessarily be (as it is
occluded by the toy). Similarly, we used the nose (one of the 18 body
parts detected) to operationalize face presence, as any half of a face
necessarily contains a nose.

@@

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose); thus the face
presence analyses to follow all result from MTCNN detections. We found
that although MTCNN and OpenPose perform comparably with the random
sample, MTCNN performed better on the high density sample (specifically
looking at precision), suggesting that OpenPose generated more false
positives than MTCNN. ViolaJones performed quite poorly relative to the
other detectors especially on the random sample.

For wrist detection, OpenPose performed moderately well (F = 0.72) with
relatively high precision, but low recall on the randomly sampled set of
frames (see Table 2). We thus analyze wrist detections, with the caveat
that we are likely underestimating the proportion of wrists overall in
the datatset.

@@

\subsection{Changes in Access to Faces and
Hands}\label{changes-in-access-to-faces-and-hands}

@@

\subsection{Access to Faces and Hands During Labeling
Events}\label{access-to-faces-and-hands-during-labeling-events}
